\chapter{Service and Support}

\section{Product Warranty}
\label{sec:产品质量保证书}

Without prejudice to any claim the {\User} may have in relation to the dealer or retailer,  the {\User} shall be granted a manufacturer's warranty under the conditions set out below:

Within 12 months from the date of delivery of the equipment and its components to the customer (Not exceeding 15 months from shipment), {\TheCompany} shall provide necessary spare parts for defects caused by poor manufacturing and/or materials, and the {\User} shall provide working hours to replace or repair related parts under the guidance of {\TheCompany}'s professional technicians.

If the equipment defect is caused by improper handling by the {\User} and/or failure to follow the relevant information described in {\ThisBook}, {\TheCompany} shall not be liable for product quality assurance. This {\TheSec} shall not apply to or does not extend to maintenance (such as installation, configuration,and software downloads) performed by authorized dealers or {\Users} themselves. The {\User} must provide purchase receipt, together with the date of purchase as evidence for invoking {\TheSec}. Ownership of equipment or components replaced by or returned to {\TheCompany} shall vest in {\TheCompany}.

Any other claims resulting out of or in connection with the equipment are not included in the scope of this {\TheSec}. No clause in this {\TheSec} attempts to limit or exclude the statutory rights of {\Users}, or the manufacturer’s liability for personal injury or death caused by its negligence. The duration of this {\TheSec} shall not be extended by services rendered under the terms of this {\TheSec}. Insofar as no warranty default exists in this {\TheSec}, {\TheCompany} reserves the right to charge {\Users} for replacement or maintenance. The above provisions do not imply a change in the burden of proof to the detriment of {\Users}.

\section{Disclaimer}

This Warranty will be invalid if the equipment defect is caused by improper handling or failure to follow the relevant information described in the user manual, including but not limited to production loss or damage to other production equipment. 

Our company is committed to continuously improving the reliability and performance of the products, and therefore reserves the right to upgrade the products. The information contained in {\ThisBook} is subject to change without notice. 

Our company strives to ensure the accuracy and reliability of the contents of {\ThisBook}, but is not responsible for any accidents and injuries caused by any errors or omissions. In particular, failures caused by the following conditions are not covered by this warranty:


\begin{enumerate}
    \item Failure to follow the user manual during installation, wiring, and connection to other control devices. 
    \item Using products beyond the specifications or standards of the manual.
    \item The storage method and working environment are beyond the appointed range (e.g. pollution, salt injury and moisture con­ densation).
    \item Products' damages caused by improper transportation.
    \item The damage caused by accidents or collisions due to failure to follow the operation and warning information.
    \item The damage caused by any third­party which is not the integrator or professional technician designated by {\TheCompany} while reconstructing, adjusting, or repairing the original components. 
    \item Changes or damage to the software or internal data.
    \item The damage caused by natural disasters including fires, earthquakes, tsunamis, lightning, high winds, and flooding.

\end{enumerate}

According to \prettyref{sec:产品质量保证书}, {\TheCompany} only undertakes to guarantee against the flaws and defects in the products and components sold directly by {\TheCompany} or its designated or authorized distributors.
The Company shall not be liable for any form of direct or indirect damage/consequences arising from other related products.